
\cvsection{Professional Experience}
\begin{cventries}
\cventry
    {CAE Software Developer}
    {GNS mbH}
    {Braunschweig, Germany}
    {Since May 2013 }
    {
      \begin{cvitems}
        \item {Design and Development of „Animator4“. It is a post-processor for a wide range of finite element analysis (FEA) applications.}
        \item {Develop efficient algorithms and data structures to handle extremely large finite element models.}
        \item {Responsible for development and maintenance of diverse FEM Data parser programs (e.g., HDF5, ASCII, binary with and without vendor API, XML, etc,.).}
        \item {Develop highly customizable graphical user interface using Qt5.}
        \item {Develop OpenGl Shaders for 3D Graphics.}
        \item {Successfully used tools like intel-vtune and gpreftools to make CPU benchmark and solve performance issues.}
        \item {Routinely use ASAN and Valgrind:Memchek to detect memory-management issues.}
        \item {Implemented a CAE NURBS to FEA Mesh converter algorithm.}
        \item {Responsible for the Nightly Build and Test System supervision.}
        \item {Deputy release manager.}
      \end{cvitems}
    }

\cventry
    {Software Engineer}
    {Silver-Atena Electronics Systems }
    {Bangalore, India}
    {July 2007 -  August 2010 }
    {
      \begin{cvitems}
        \item {Underwent an intensive training about Software test techniques in Avionic Software Systems.}
        \item {Implemented the "Ignored Returns" and "Function Flow Chart" algorithm for an in-house C-code static analyses tool.}
        \item {Automated the signal data range test-case generation for an avionic-system-test project.}                       
      \end{cvitems}
    }
\end{cventries}


